Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 manuscript.Rmd
Make all directory creation recursive

# create subdirectories
dir.create("./data/raw") # load three data files here
dir.create("./data/formatted/primary")
dir.create("./data/formatted/secondary")
dir.create("./results/primary/crqa")
dir.create("./results/primary/windowed-crqa")
dir.create("./results/secondary/icews/crqa/source_target")
dir.create("./results/secondary/icews/crqa/target")
dir.create("./results/secondary/icews/windowed-crqa/source_target")
dir.create("./results/secondary/icews/windowed-crqa/target")
dir.create("./results/secondary/phoenix/crqa/source_target")
dir.create("./results/secondary/phoenix/crqa/target")
dir.create("./results/secondary/phoenix/windowed-crqa/source_target")
dir.create("./results/secondary/phoenix/windowed-crqa/target")

>>>>

# create subdirectories
dir.create("./data/raw") # load three data files here
dir.create("./data/formatted/primary", recursive = TRUE)
dir.create("./data/formatted/secondary/icews", recursive = TRUE)
dir.create("./data/formatted/secondary/phoenix", recursive = TRUE)
dir.create("./results/primary/crqa", recursive = TRUE)
dir.create("./results/primary/windowed-crqa", recursive = TRUE)
dir.create("./results/secondary/icews/crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/icews/crqa/target", recursive = TRUE)
dir.create("./results/secondary/icews/windowed-crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/icews/windowed-crqa/target", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/phoenix/crqa/target", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa/source_target", recursive = TRUE)
dir.create("./results/secondary/phoenix/windowed-crqa/target", recursive = TRUE)
